Continuous Generalization of Buildings

### 2017-01-13 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
wrote some instructions in ReadMe.docx

Our generalisation is as follows. We buffer buildings with 
radius $d+r-r_0$, then we buffer the results with $-d$. In order 
to 
remove some spikes from the buffering, we buffer the results 
with $-\epsilon$, and then again with $\epsilon$. We simply set 
$\epsilon=\frac{1}{10}d$. After these buffering operations, we 
eliminate the buildings with area less than $d^2$.

>>>>

Our generalisation is as follows. We buffer buildings with 
radius $d+r-r_0$, and merge the buffers overlapping each 
other.
Then we buffer the results with $-d$.
In order to 
remove some spikes from the buffering, we buffer the new results 
with $-\epsilon$, and then again with $\epsilon$. We simply set 
$\epsilon=\frac{1}{10}d$. After these buffering operations, we 
eliminate the buildings with area less than $d^2$.
